\cvsection{Publications}

\cvsubsection{Selected}

\begin{cvpubs}

\cvpub{\honorpositionstyle{Fernando Zhapa-Camacho}, Zhenwei Tang, Maxat Kulmanov, Robert Hoehndorf. 2024. Predicting protein functions using positive-unlabeled ranking with ontology-based priors. ISMB 2024.}

\cvpub{\honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf. 2024. Lattice-preserving ALC ontology embeddings. NeSy 2024.}

\cvpub{Jiaoyan Chen, Olga Mashkova, \honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf, Yuan He, Ian Horrocks. 2024. Ontology Embedding: A Survey of Methods, Applications and Resources. Preprint.}

\cvpub{\honorpositionstyle{Fernando Zhapa-Camacho}, Maxat Kulmanov, Robert Hoehndorf. 2023. mOWL: Python library for machine learning with biomedical ontologies. Bioinformatics, Volume 39, Issue 1.}

\cvpub{\honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf. 2023. From axioms over graphs to vectors, and back again: evaluating the properties of graph-based ontology embeddings. NeSy 2023.}

\end{cvpubs}

\cvsubsection{Additional}

\begin{cvpubs}

\cvpub{Azza Althagafi, \honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf. 2024. Prioritizing genomic variants through neuro-symbolic, knowledge-enhanced learning. Bioinformatics, Volume 40, Issue 5.}

\cvpub{\honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf. 2023. Evaluating Different Methods for Semantic Reasoning Over Ontologies. SemREC 2023.}

\cvpub{Sarah M. Alghamdi, \honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf. 2022. A-LIOn - Alignment Learning through Inconsistency negatives of the aligned Ontologies. The 17th International Workshop on Ontology Matching.}

\cvpub{Maxat Kulmanov, \honorpositionstyle{Fernando Zhapa-Camacho}, Robert Hoehndorf. 2021. DeepGOWeb: fast and accurate protein function prediction on the (Semantic) Web. Nucleic Acids Research.}

\cvpub{Joseph R. González, \honorpositionstyle{Fernando Zhapa-Camacho}, Oscar V. Guarnizo, Francisco Ortega-Zamorano. 2018. Successive Adaptive Linear Neural Modeling for Equidistant Real Roots Finding. ETCM 2018.}

\end{cvpubs}